%========================================================================================
% GenAI Engineer Resume - Himanshu Gohil
% Clean, ATS-Friendly LaTeX CV
%========================================================================================

\documentclass[11pt, a4paper]{article}

% --- Packages ---
\usepackage[margin=0.5in, top=0.4in, bottom=0.4in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage{fontawesome5}
\usepackage{parskip}
\usepackage{multicol}
\usepackage{ragged2e}

% --- Color Palette ---
\definecolor{accentblue}{HTML}{1A73E8}
\definecolor{darkgray}{HTML}{2D2D2D}
\definecolor{midgray}{HTML}{555555}
\definecolor{rulegray}{HTML}{CCCCCC}

% --- Hyperlink Styling ---
\hypersetup{
    colorlinks=true,
    urlcolor=accentblue,
    linkcolor=accentblue,
}

% --- Section Title Formatting ---
\titleformat{\section}{
    \vspace{-4pt}\color{accentblue}\large\bfseries\uppercase
}{}{0em}{}[\color{rulegray}\titlerule\vspace{-2pt}]

\titlespacing*{\section}{0pt}{8pt}{4pt}

% --- Custom Commands ---
\newcommand{\resumename}[1]{%
    {\Huge\bfseries\color{darkgray} #1}\par
}

\newcommand{\tagline}[1]{%
    \vspace{2pt}{\large\color{midgray} #1}\par
}

% Job Entry Command: {Company}{Location}{Title}{Date Range}{Bullets}
\newcommand{\jobentry}[5]{%
    \vspace{2pt}
    \noindent
    \begin{tabularx}{\textwidth}{@{}X r@{}}
        {\bfseries\color{darkgray} #3} & {\small\color{midgray} #4} \\
        {\color{accentblue} #1} \textnormal{{\small\color{midgray}$\cdot$ #2}} & \\
    \end{tabularx}
    \vspace{-4pt}
    \begin{itemize}[leftmargin=1.2em, itemsep=1pt, parsep=0pt, topsep=2pt, nosep, label=\textbullet]
        #5
    \end{itemize}
}

% Education Entry: {Degree/Cert}{Institution}{Detail}{Date}
\newcommand{\eduentry}[4]{%
    \vspace{2pt}
    \noindent
    \begin{tabularx}{\textwidth}{@{}X r@{}}
        {\bfseries\color{darkgray} #1} & {\small\color{midgray} #4} \\
        {\color{midgray}\small #2 $\cdot$ #3} & \\
    \end{tabularx}
}

% Skill Category
\newcommand{\skillcat}[2]{%
    \noindent{\bfseries\color{darkgray} #1:} {\color{midgray} #2}\par\vspace{1pt}
}

% Project Entry: {Name}{Tech Stack}{Bullets}
\newcommand{\projectentry}[3]{%
    \vspace{2pt}
    \noindent{\bfseries\color{darkgray} #1} \textnormal{{\small\color{accentblue}[#2]}}\\
    \vspace{-4pt}
    \begin{itemize}[leftmargin=1.2em, itemsep=1pt, parsep=0pt, topsep=2pt, nosep, label=\textbullet]
        #3
    \end{itemize}
}

%========================================================================================
\begin{document}
\pagestyle{empty}

%--- HEADER -----------------------------------------------------------
\begin{center}
    \resumename{Himanshu Gohil}
    \tagline{GenAI Specialist | Cloud Architect}
    \vspace{4pt}
    \small
    \faIcon{map-marker-alt}~Mumbai, India \quad
    \faIcon{phone}~+91 90822 33297 \quad
    \faIcon{envelope}~\href{mailto:himanshugohil234@gmail.com}{himanshugohil234@gmail.com} \\[2pt]
    \faIcon{linkedin}~\href{https://linkedin.com/in/tghimanshu}{linkedin.com/in/tghimanshu} \quad
    \faIcon{github}~\href{https://github.com/tghimanshu}{github.com/tghimanshu} \quad
    \faIcon{code}~\href{https://leetcode.com/himanshu_gohil_12}{leetcode.com/himanshu\_gohil\_12}
\end{center}

%--- PROFESSIONAL SUMMARY ---------------------------------------------
\section{About Me}
\begin{justify}
GenAI engineer with \textbf{3.5 years of experience} spanning software development, cloud infrastructure, and applied AI. Spent two years at \textbf{Google} building prototypes and consulting enterprise customers, which gave me a grounded understanding of what real-world AI adoption involves --- including the gaps between what models can do and what businesses actually need. Deeply engaged in the evolving GenAI landscape, with a current focus on solving the practical last-mile challenges of agent workflows and data pipelines for the \textbf{US Energy Sector} at Go Digital.
\end{justify}

%--- EXPERIENCE -------------------------------------------------------
\section{Experience}

\jobentry
    {Go Digital Technology Consulting}
    {Mumbai, India}
    {Senior Engineer}
    {Aug 2025 -- Present}
    {
        \item Build GenAI applications and data analytics solutions for the \textbf{US Energy Sector}, focusing on automating data extraction workflows and accelerating internal research cycles.
        \item Architect data pipelines over company-owned datasets, enabling teams to move from raw data to decision-ready insights without manual intervention.
        \item Consolidate key business metrics into a central \textbf{visualization platform}, eliminating tool fragmentation and giving stakeholders a single, reliable view of operational data.
        \item Research autonomous agent frameworks and the integration of Medallion architecture with LLM-based workflows --- translating findings into concrete architectural recommendations for the team.
        \item Serve as the technical bridge between engineering and stakeholders, ensuring AI roadmap decisions are grounded in actual business needs rather than just what the technology can do.
    }

\jobentry
    {Google}
    {Mumbai, India}
    {Project Management Apprentice (GenAI Specialist)}
    {Jul 2023 -- Jul 2025}
    {
        \item Built \textbf{28 prototypes} demonstrating Google Cloud and Vertex AI capabilities to enterprise customers across Retail, Automobile, and Media --- mostly in Python and Next.js.
        \item Worked directly with \textbf{6 customers} on troubleshooting and Cloud consulting, which gave me a good ground-level understanding of real adoption challenges.
        \item Helped set up dashboards for Revenue Forecasting and Cloud Blockers that gave visibility to \textbf{600+ customers} and touched \textbf{\$200M+} in tracked revenue.
        \item Contributed as a front-end engineer on an internal social platform using Angular, with a Spring Boot backend.
        \item Automated repetitive processes across \textbf{11 internal teams}, cutting down manual work by around \textbf{95\%}.
    }

\jobentry
    {Go Digital Technology Consulting Pvt. Ltd.}
    {Mumbai, India}
    {Associate Software Engineer}
    {Jun 2022 -- Jul 2023}
    {
        \item Migrated several on-premises web applications to the cloud, resulting in roughly \textbf{60\% improvement} in performance post-migration.
        \item Modernized SharePoint workflows, reducing manual steps by \textbf{80\%} and achieving \textbf{93\%} user satisfaction in internal surveys.
        \item Built web applications for field teams to log and track on-ground concerns, improving operational efficiency by \textbf{60\%} and concern visibility by \textbf{40\%}.
        \item Received the \textbf{Client Communications Award} for building strong, trust-based relationships with client teams.
    }

%--- TECHNICAL SKILLS -----------------------------------------------------------
\section{Technical Skills}

\skillcat{Core LLMs}{\mbox{Gemini Enterprise}, \mbox{Claude (Anthropic)}, \mbox{GPT-4 via Azure}, \mbox{AWS Bedrock} (Titan, Llama)}
\skillcat{Agent Frameworks}{\textbf{\mbox{Google ADK}}, LangChain, \mbox{DialogFlow CX}, \mbox{Vertex AI Agents}}
\skillcat{RAG \& Vector}{\mbox{BigQuery Vector Search}, \mbox{Vertex AI Matching Engine}, \mbox{Embeddings API}, \textbf{\mbox{Medallion Architecture}}}
\skillcat{Cloud \& DevOps}{GCP (primary), AWS, Firebase, Docker, Terraform, \mbox{GitLab CI}, \mbox{GitHub Actions}}
\skillcat{Development}{Python (Flask, Streamlit, Dash), TypeScript, JavaScript, Angular, \mbox{React (NextJS)}, \mbox{Apps Script}}
\skillcat{Databases}{BigQuery, PostgreSQL, MySQL, MongoDB, GoogleSQL}
\skillcat{Process \& Tools}{Jira, Asana, Notion, Agile/Scrum, \mbox{Vertex AI Studio}, \textbf{\mbox{Model Armor}}}

%--- KEY PROJECTS -----------------------------------------------------
\section{Projects}

\projectentry
    {AI Agent Workflows}
    {Vertex AI, Python, ADK, Gemini API, GCP}
    {
        \item Built and tested several AI agents using Google's Agent Development Kit (ADK) with \textbf{function calling} and tool-use --- including API integrations, structured data lookup, and media processing tasks like automated subtitling and call transcript analysis.
        \item Learned a lot about how multi-step agent reasoning works in practice, especially where it breaks down: tool invocation failures, hallucinated function arguments, and when to add guardrails vs.\ simplify the task definition.
    }

\projectentry
    {Internal BI Dashboard}
    {Python, Streamlit, Plotly Dash, BigQuery, GCP}
    {
        \item Designed a multi-source data pipeline that normalized and joined across \textbf{heterogeneous internal datasets} in BigQuery, handling schema inconsistencies and incremental refresh logic to keep dashboards current without full reloads.
        \item Built the frontend in Streamlit and Plotly Dash with parameterized filters and drill-down views --- keeping the query layer decoupled from the UI so non-technical stakeholders could explore data without writing SQL.
    }

\projectentry
    {Model Armor Early Adoption}
    {GCP, Python, Vertex AI, Model Armor}
    {
        \item Picked up Model Armor when it first launched and implemented it for a few compliance-sensitive demos in the HCLS and BFSI space.
        \item Also worked on \textbf{10+ GenAI demos} across Retail, Media, and Automobile as part of the Google Cloud customer engagement work.
    }


%--- EDUCATION & CERTIFICATIONS --------------------------------------------------------
\section{Education \& Certifications}

\eduentry
    {B.Sc. in Information Technology}
    {Ghanshyamdas Saraf College, Mumbai}
    {SGPA: 9.32 | Board of Studies (Alumni) | Technical Fest Head}
    {2019 -- 2022}

\vspace{4pt}
\noindent{\bfseries\color{darkgray} Professional Certifications} \hfill {\small\color{midgray} 2023 -- 2025}\\[2pt]
\begin{multicols}{2}
\begin{itemize}[leftmargin=1.2em, itemsep=1pt, parsep=0pt, topsep=0pt, label={\color{midgray}$\cdot$}]
    \item {\color{midgray}\small GCP Professional Cloud Architect}
    \item {\color{midgray}\small GCP Associate Cloud Engineer}
    \item {\color{midgray}\small GCP Cloud Digital Leader}
    \item {\color{midgray}\small GCP Generative AI Leader}
    \item {\color{midgray}\small OCI 2025 Generative AI Professional}
    \item {\color{midgray}\small Project Management Course --- Google}
\end{itemize}
\end{multicols}

%--- AWARDS -----------------------------------------------------------
\section{Awards \& Extras}

\begin{itemize}[leftmargin=1.2em, itemsep=2pt, parsep=0pt, topsep=2pt]
    \item \textbf{Client Communications Award} --- Go Digital, 2023, for building strong relationships and clear communication with client teams
    \item \textbf{Google Project Management Certificate} --- completed during the Google apprenticeship program
    \item \textbf{Languages} --- English, Hindi, Gujarati, Marathi
\end{itemize}

\end{document}
